Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2017-07-05 workflow/workflow.Rmd
fix plotBarplot

```{r addPublishedClusters, fig.cap="Barplot of number of cells per cluster, for original published clustering."}
ceObj<-addClusters(ceObj, colData(ceObj)$publishedClusters, 
                   clusterLabel = "publishedClusters")
plotBarplot(ceObj,whichClusters=c("mergeClusters","publishedClusters")) 
```

>>>>

```{r addPublishedClusters, fig.cap="Barplot of number of cells per cluster, for original published clustering."}
ceObj<-addClusters(ceObj, colData(ceObj)$publishedClusters, 
                   clusterLabel = "publishedClusters")
plotBarplot(ceObj,whichClusters=c("combineMany","publishedClusters")) 
```
